% universal settings
\documentclass[a4paper,12pt,oneside]{article}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[osf]{Alegreya,AlegreyaSans,FiraMono}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{xcolor}

\usepackage[tracking=true, letterspace=50]{microtype}
\usepackage[left=1.7in, right=1.7in, top=1in, bottom=1.25in]{geometry}
\usepackage{setspace}
\usepackage{calc}

% basic global settings
\setlength{\parindent}{0em}
\linespread{1.15}
\SetTracking{encoding=*,shape=sc}{50}
\setlist[itemize]{itemsep=0em}

% title format
\makeatletter
\def\maketitle{\noindent{
\vspace{0.6in}
    \begin{center}
      {\textls[120]{\LARGE \selectfont \textsc{\sffamily \MakeLowercase \@title} \par}}%
      \vskip 1.2em
      \small \textls{\selectfont \textsc{\sffamily \MakeLowercase \residence}} \par
      \vskip 0.5em
      \small \textls{\selectfont \sffamily \MakeLowercase{\phone\ | \href{mailto:\email}{\email}\ | \href{http://\homepage}{\homepage}}}
      \vskip 2em
    \end{center}
  }
}
\makeatother

% metadata
\title{Ramakrishnan R.\,Iyer}
\newcommand{\residence}{202, Siri Fortune, 18\textsuperscript{th} Cross, Purnapragna Layout, Bangalore, KA 560061}
\newcommand{\phone}{+91~886~106~5751}
\newcommand{\email}{ram.iyer@outlook.in}
\newcommand{\homepage}{ramiyer.me}

% styling classes
\newcommand{\organisation}[3]{\vspace{1.7em}{\large{#1 \hfill #2}} \par \vspace{0.3em} \textit{#3} \vspace{0.4em}}
\titleformat{\section}{\sffamily \AlegreyaSansMedium \scshape \MakeLowercase}{\thesection}{}{\hrule}
\titlespacing\section{0em}{2.25em}{-1em}
\renewcommand{\UrlFont}{\ttfamily\footnotesize}

% format links
\hypersetup{
    colorlinks,
    linkcolor={red!50!black},
    urlcolor={red!50!black}
}

\pagenumbering{gobble}

\begin{document}
  \maketitle

  I am an \emph{Automation Expert}, drawn to simplifying operations. I specialise in IT\,Infrastructure automation, including end-to-end automated server build workflow. I am also a \emph{published co-author} of a book on PowerShell.

  \section*{Experience}

  \organisation{Merck Group}
      {2019~--~present}
      {Expert, Infra. Automation}
  
  I work in the internal IT Infrastructure Automation team (Foundations and Ecosystem) of the vibrant science and technology company. We work on automation projects across the Windows Infrastructure space.

  \begin{itemize}
      \item Our prime focus area is the automation of server build and immutable configuration using Infrastructure as Code (IaC) concepts, PowerShell, \textsc{sql}\,Server, Packer, Azure DevOps and PowerShell \textsc{dsc}.
      \item We help Operations and other teams automate repetitive tasks.
  \end{itemize}

  \organisation{Cognizant Technology Solutions}
      {2010~--~2019}
      {Infra. Technology Specialist}

  I lead the offshore Infrastructure team for a renowned paper manufacturer in the US. I cut across the infrastructure fabric for the client, including VMware, Nutanix, Exchange, \textsc{scom}, \textsc{sccm} and Citrix.

  \begin{itemize}
      \item I specialise in PowerShell; built modules, with tens of functions for backup, clean-up, auto-healing, auditing, and disaster recovery.
      \item I have led implementations of \textsc{scom}, \textsc{sccm}, Citrix XenApp~7.15, \textsc{dmarc}, etc. Ask me about my experience with the projects.
  \end{itemize}

  \section*{Off-work}

  \organisation{PowerShell Core for Linux Administrators Cookbook}
  {2018}
  {Co-author, Packt Publication}

  The offer to co-author a book on two things I love, excited me. After a fruitful journey of over six months, the book, \href{https://amzn.to/2PwxR18}{PowerShell Core for Linux Administrators Cookbook}, was released in November 2018.

  \organisation{Meraki Post}
  {2015~--~present}
  {IT Architect, Book reviewer, Podcaster (because, passion)}

  A few of us friends started a book review site, \href{https:\\www.merakipost.com}{Meraki Post}. It has been a journey to better control, performance and UX, with Jekyll, GitLab~CI, \textsc{aws}~S3, CloudFront and Slack. Ask me about what I built!

  \organisation{The Weekend Lab}
  {2017~--~present}
  {All work and no play makes~...}

  \begin{itemize}[topsep=0em]
      \item I tinker with the world-favourite Raspberry PI~3 B+, running Arch Linux (\textsc{arm}). Currently, it is our Media Server at home.
      \item Writing is my passion, too. Links to my blogs, podcast, stories and books are available on my homepage, \url{https://ramiyer.me}.
      \item I also built a detailed, online version of this résumé using Liquid and Jekyll Collections, available at \url{https://resume.ramiyer.me}.
  \end{itemize}

  \section*{Education}

  \organisation{Birla Institute of Technology and Science, Pilani}{2017}{M.Tech (Software Engineering, Work-Integrated)}

  I dipped my feet into Cloud Computing and IaC here. 18 of our clients benefited from the \textsc{gui}-based tool for Windows administration that I built using PowerShell, for my dissertation.

  \organisation{Alpha Arts and Science College, Chennai}{2010}{B.Sc (Electronics and Communications)}

  During my stint here, I served as the \emph{President} of the Students’ Forum, as well as the \emph{Editor} of our departmental journal. I graduated as the \emph{Best Outgoing Student} of the batch, along with a University rank in my Majors.
\end{document}
